---
title: "Homework_3"
author: "Rutwik Guntoorkar - rutwik.guntoorkar@rutgers.edu"
date: "9/22/2022"
output: html_document
---

```{r}
library(fpp)
library(fpp2)
data()
table(debitcards)



```
```{r}
head(debitcards)
```
```{r}
plot(debitcards,main = "Retail debit card usage in Iceland", xlab = "Years", ylab="Monthly retail debit card usage in Iceland (In Millions")
```

#Conclusion : 
•Plot shows upper trend pattern in usage data.
•We can see a small seasonality going up every year.
•After studying this plot we can infer that:
∙Acf plot should have significant values.
∙There might be a wave visual of the correlation depicting the seasonal change in the data.


```{r}
Acf(debitcards, main = "ACF plot - Debit cards Usage in Iceland")
```
#Conclusion : 
•This shows that the historic data has significant impact on the preceding data.
•Predicted small seasonality can be seen in ACF plot


```{r}
practice <- HoltWinters(debitcards)
attributes(practice)
```



```{r}
plot(practice)
```
#Conclusion : 
•As seen above Holt winters algorithm is deviating at multiple points.
•Which indicates tuning must be done for alpha, beta, gamma values.

```{r}
practice_f <- forecast(practice)
attributes(practice_f)
```


```{r}
plot(practice_f$residuals, main = "Residuals")
```




```{r}
hist(practice_f$residuals, main = "Residuals - Histogram")
```

#Conclusion : 
The histogrm plot shows normal distribution for residual

```{r}
Acf(practice_f$residuals, main = "Residuals - Acf Plot")
```
#Conclusion : 
As there are four lines crossing confidence internal line, there is significant difference and the residuals can be predictable.


```{r}
accuracy(practice_f)
```
#Conclusion : 
As per ARIMA model:
As MPE value is close to 0, The forecast is unbiased.
As RMSE as well is close to 0, the forecast predicted is good.